### 2018-04-16 includes/experiment.tex
Adjusting some text and adding a reference.

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others. These suites are
\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
conducted in series, each with a timeout of 15 seconds,
on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
        \caption{Performance on \textit{Concats-Extracts-Small}}
        \label{fig:concats-extracts-small}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
        \caption{Performance on \textit{Different-Prefix}}
        \label{fig:different-prefix}
    \end{subfigure}
    \caption{Instances hard for \cvc{}}
    \label{fig:cvc-hard}
    \bigskip
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
        \label{fig:concats-balanced}
        \caption{Performance on \textit{Concats-Balanced}}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-big.png}
        \label{fig:concats-big}
        \caption{Performance on \textit{Concats-Big}}
    \end{subfigure}
    \caption{Instances hard for \us{}}
    \label{fig:z3str3-hard}
\end{figure}

@@

\fuzzer{}'s ability to produce scaling instances helped uncover several
implementation issues and performance limitations in \us{}. Scaling inputs
can reveal issues that would normally be out of scope for unit tests or
industrial benchmarks. Three different
performance and implementation bugs were identified and fixed in \us{}
as a result of testing with the \fuzzer{} scaling suites
\textit{Lengths} and \textit{Concats}.

\fuzzer{} also helped identify a number of performance-related issues and
opportunities for new heuristics in \us{}. For example, by examining \us{}'s
execution traces on the
instances in the \textit{Concats} suite we discovered a
potential new heuristic. In particular, \us{} does not
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among sub-terms. \us{}
therefore introduces a large number of unnecessary intermediate
variables and propagations.

>>>>

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others.\footnote{Only the
results that made one solver perform poorly and not others are presented, but
results for all \fuzzer{} suites are available on the \fuzzer{}
website\cite{website}.}
They are \theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
conducted in series, each with a timeout of 15 seconds,
on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
        \caption{Performance on \textit{Concats-Extracts-Small}}
        \label{fig:concats-extracts-small}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
        \caption{Performance on \textit{Different-Prefix}}
        \label{fig:different-prefix}
    \end{subfigure}
    \caption{Instances hard for \cvc{}}
    \label{fig:cvc-hard}
    \bigskip
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
        \label{fig:concats-balanced}
        \caption{Performance on \textit{Concats-Balanced}}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{data/graphs/concats-big.png}
        \label{fig:concats-big}
        \caption{Performance on \textit{Concats-Big}}
    \end{subfigure}
    \caption{Instances hard for \us{}}
    \label{fig:z3str3-hard}
\end{figure}

@@

\fuzzer{}'s ability to produce scaling instances helped uncover several
implementation issues and performance limitations in \us{}. Scaling inputs
can reveal issues that would normally be out of scope for unit tests or
industrial benchmarks. Three different
performance and implementation bugs were identified and fixed in \us{}
as a result of testing with the \fuzzer{} scaling suites
\textit{Lengths-Long} and \textit{Concats-Big}.

\fuzzer{} also helped identify a number of performance-related issues and
opportunities for new heuristics in \us{}. For example, by examining \us{}'s
execution traces on the
instances in the \textit{Concats-Big} suite we discovered a
potential new heuristic. In particular, \us{} does not
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among sub-terms. \us{}
therefore introduces a large number of unnecessary intermediate
variables and propagations.

### 2018-04-16 includes/introduction.tex
Removing redundant text.
Removing some redundant text to make space for shifted Contributions title.
Adjusting some text and adding a reference.

\subsubsection{Contributions}\footnote{All source code, problem suites, and supplementary material
referenced in this paper are available at the \fuzzer{} website \cite{website}.}
\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regex
        instances. Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.

>>>>

\newpage
\subsubsection{Contributions}\footnote{All source code, problem suites, and
supplementary material referenced in this paper are available at the
\fuzzer{} website \cite{website}.}
\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regex
        instances. Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.
